Measurement and Analysis of Child Pornography Trafficking on P2P Networks\nocite{Hurley}

### 2013-10-15 Paper_presentation.tex
Novas imagens

@@

>>>>

\begin{block}{Other details}

\item[\checkmark]Gnutella allows a peer to be browsed, so investigators can enumerate all files shared.

\item[\checkmark]Gnutella Browse dataset consists peer browses, not just FOI, but some Gnutella peers cannot be browsed (client configuration).

\item[\checkmark]eMule does not permit browses, so each of these datasets includes only peers that share FOIs;

\begin{block}{Other details}

\item[\checkmark]A GUID’s library is the set of files that were observed being shared by that GUID on a given day.

\item[\checkmark]A GUID’s corpus is the set of all files shared by that GUID over the entire duration of the study.

@@

\begin{block}{A comparison of Peer Behavior}

\begin{figure}[!htb]
\centering
\includegraphics[scale=0.35]{CDF_characterization_emule}
\caption{Cumulative distribution function (eMule)}.
\label{fig:CDF_characterization_emule}
\end{figure}

\begin{block}{A comparison of Peer Behavior}

\begin{figure}[!htb]
\centering
\includegraphics[scale=0.35]{CDF_characterization_gnutella}
\caption{Cumulative distribution function (Gnutella)}.
\label{fig:CDF_characterization_gnutella}
\end{figure}
